---
title: "Experiment 2C: Visual interference disrupts verbal cueing of visual recognition but not word repetition detection"
author: "Pierce Edmiston"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: true
---

Experiment 2C was conducted to test the hypothesis that the effect of 
visual interference in Experiments 2A and 2B was limited to a disruption
of visual knowledge and not a disruption of auditory processing of the
verbal cues. In this experiment, participants were played auditory cues
with or without visual interference and afterward they either had to
perform the upright picture detection task as in Experiments 2A and 2B
or instead they were presented a printed word and had to verify if the
printed word was the same as the verbal cue. We expected the effect
of visual interference to be limited to performance on the image recognition
task and not to have an impact on word repetition detection since on our view
only the verbal cueing of visual recognition requires visual knowledge
that is susceptible to visual interference.

```{r, echo = FALSE, message = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.path = 'experiment2c-figs/'
)

read_chunk("models/unilateral.R")
```

```{r, setup}
```

# Methods

## Participants

`r n_subjs` participants received course credit for participating in the 
experiment.

```{r}
unilateral %>%
  group_by(version) %>%
  summarize(N = length(unique(subj_id)))
```

```{r, subjs}
```

## Materials and Procedure

Experiment 2C was similar to Experiment 2A except that on a subset of trials
(25%) instead of two pictures a single word appeared, presented unilaterally. 
Which side the word appeared did not matter; participants
pressed the up arrow if the printed word was the same as the word they heard.
They pressed the down arrow if the printed word was not a repetition. Of
these word trials, 75% of the time the printed word was a repetition of
the auditory cue.

Participants were allowed to respond with any of the four arrow keys
on each trial. After initial data collection (N = 14), we revised the task
to disallow left or right responses on word repetition trials.

To allow for the additional word repetition task which required a verbal cue
to be played on every trial, we also excluded the 
baseline, noise cues that were presented in Experiments 2A and 2B.

# Results

```{r, overall-plot}
```

```{r, overall-error-plot}
```

## Effect of visual interference on verbal cueing of image recognition

In a replication of Experiments 2A and 2B, we observed a cueing effect in RTs on
the trials without any visual interfence, [stats]. Visual interference reduced
this cueing effect by 40%, [stats]. No cueing effect in accuracies was observed
on the trials without any visual interference, [stats].

```{r, pic-nomask-mod, echo = 1:2}
```

```{r, pic-mod, echo = 1:2}
```

```{r, pic-error-nomask-mod, echo = 1:2}
```

```{r, pic-error-mod, results = "hide"}
```

## Effect of mask on word repetition

Visual interference did not have a detrimental effect on the speed, [stats], or
accuracy, [stats], at which repeated words were detected.

```{r, word-mod, echo = 1:2}
```

```{r, word-error-mod, echo = 1:2}
```

## Correlation between interference effects

If visual interference disrupted processing of the verbal cues in general
than we might expect those individuals who were most affected by the 
interference on the upright image recognition trials to also be affected 
on the word repetition trials, i.e., we would expect a correlation between
the effect of the mask in the two tasks. However, the effect of the visual
interference on the upright image detection task was independent of its
effect on the word repetition task, [stats], supporting the hypothesis that the
effect of visual interference is specific to tasks requiring visual knowledge.

```{r, mask-correlation-plot}
```

```{r, mask-correlation-mod, echo = 1}
```

# Discussion
