---
title: "Experiment 2C: Orientation discrimination with word repetition"
author: "Pierce Edmiston"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: true
---

```{r, echo = FALSE, message = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.path = 'experiment2c-figs/'
)

read_chunk("models/unilateral.R")
```

```{r, setup}
```

# Methods

## Materials

The same materials were used in Experiment 2C as were used in Experiments 2A-B.

## Participants

```{r}
unilateral %>%
  group_by(version) %>%
  summarize(N = length(unique(subj_id)))
```

```{r, subjs}
```

## Procedure

On most trials (75%), participants heard a cue and saw two images, one of which
was upside down. Their task was to identify the correctly oriented image 
as quickly as possible using the left or right arrow keys on the keyboard. In
Experiment 2C all cues were spoken words, i.e., no white noise cues were used.

On some trials (25%), instead of two pictures a single word appeared, presented
unilaterally. Which side the word appeared did not matter; participants
pressed the up arrow if the printed word is the same as the word they heard.
They pressed the down arrow if the printed word is not a repetition.

Participants were allowed to respond with any of the four arrow keys
on each trial, and were reminded of the keys to use if they made
a key type error (for example, pressing the left or right arrow
on a word trial in which the correct response is either up or down). 
After initial data collection (N = 14), we revised the task to disallow
left or right responses on word repetition trials.

# Results

```{r, overall-plot}
```

```{r, overall-error-plot}
```

## Upright picture detection

```{r, pic-mod, echo = 1}
```

```{r, pic-error-mod, echo = 1}
```

## Word repetition

```{r, word-mod, echo = 1}
```

```{r, word-error-mod, echo = 1}
```

# Discussion
