---
title: "Orientation Words Results"
author: "Pierce Edmiston"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: true
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.path = "results-figs/"
)

library(devtools)
library(dplyr)
library(lme4)
library(broom)
library(ggplot2)

load_all("orientationwords")

orientation <- compile("experiment/data/") %>%
  clean %>% recode# %>% drop

read_chunk("models/overall.R")
```

# Overall results

## Reaction times

```{r, rt-plot}
```

## Error rates

```{r, error-plot}
```

# Orientation discrimination (replication)

## Cueing effect in reaction times

The cueing effect is *larger* on the masked trials.

```{r, cueing-effect-mod, echo = 1}
```

## Cueing effect in error rates

Looking at the error rates, the story makes more sense. 
The mask increases error rates on the valid cue trials and
decreases error rates on the invalid cue trials.

```{r, cueing-effect-errors-mod, echo = 1}
```

# Word repetition task

The mask does not have an impact on any aspect of the word repetition task.

## Reaction times

```{r, word-mod, echo = 1}
```

## Error rates

```{r, word-errors-mod, echo = 1}
```
