---
title: "Orientation Words Results: Unilateral Presentation"
author: "Pierce Edmiston"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: true
---

```{r, echo = FALSE, message = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.path = 'unilateral-figs/'
)

read_chunk("models/unilateral.R")
```

```{r, setup}
```

# Methods

On most trials, participants hear a cue and see two images, one of which
is upside down. Their task is to identify the correctly oriented image 
as quickly as possible.

On some trials, instead of two pictures a single word appears, presented
unilaterally. Which side the word appears does not matter; participants
press the up arrow if the printed word is the same as the word they heard.
They press the down arrow if the printed word is not a repetition. These
catch trials ensure that people are indeed listening to the auditory cues.

More importantly, the effect of the mask on these word trials should be
negligible if what the mask is doing is disrupting selectively visual
knowledge (necessary in order to observe a cueing effect on the baseline
trials), as opposed to in general disrupting task performance. If the mask
does not disrupt task performance in general, it should not have a
detrimental effect on word repetition detection.

More precisely, we expect the previously demonstrated effect of the mask
on upright picture detection to be independent of the effect of the mask
on word repetition detection. We investigated this at the individual level:
by looking at the correlation between the effect of the mask on the cueing
effect in the picture detection task and the effect of the mask on word
repetition trials.

# Version 1

In version 1 of the experiment, participants were allowed to respond with
any of the four arrow keys on each trial. The analysis of RTs below includes 
only the correct responses.

## RTs

```{r, unilateral1-mod, echo = 1}
```

```{r, unilateral1-plot}
```

## Errors

We next analyzed where people were making errors. For upright picture
detection, we expected the mask to reduce the cueing effect to the
extent that it was present on the nomask trials.

```{r, error-mod, echo = 1}
```

Unfortunately, the prepotent response to respond "left" when something appears on the left was responsible for many people to responding to the location of the printed word rather than it's identity, which required an up or down response.

```{r, error-plot}
```

### Types of errors

The plot below depicts the types of errors that were made on either the
upright picture detection trials or the word repetition detection trials.
Far more incorrect response types (left/right on a word repetition trial, or up/down on an upright picture trial) occured on word repetition trials.

```{r, error-type-plot}
```

# Version 2

In version 2, participants completed the same task, except that they were
only allowed to respond with the up/down arrows on the word repetition trials,
and only allowed to respond with the left/right arrows on the upright picture
orientation trials.

```{r, unilateral2-mod, echo = 1}
```

```{r, unilateral2-plot}
```

# Both versions

```{r, unilateral-mod, echo = 1}
```

```{r, unilateral-plot}
```